---
title: "workingWithDates"
format: html
editor: visual
---

```{r}
library(tidyverse)
conversions = read.csv("https://raw.githubusercontent.com/dbreynol/DS809/main/data/conversions.csv") 
```
# Data Wrangling Section


# 1. What are the top 5 countries in terms of Display Ad conversions?

```{r}
displayAdsByCountry = head(filter(conversions, marketing_channel == "Display Ads") %>%  group_by(country_code) %>% summarise(totalconversion = sum(conversions, na.rm = TRUE)) %>% arrange(desc(totalconversion)), 5)

print(displayAdsByCountry)
```

# 2. What is the distribution of US conversions by day of week (i.e., Mon - Fri)? (boxplots or histograms)

```{r}
conversionsByWeekDay = mutate(conversions, datestamp = wday(datestamp))
usConversions = filter(conversionsByWeekDay, country_code == "us") %>% filter(datestamp > 1) %>% filter(datestamp < 7) %>% group_by(datestamp) %>% summarise(tot_con = sum(conversions, na.rm = TRUE))

ggplot(usConversions, aes(x=datestamp, y=tot_con)) +
  geom_bar(stat = "identity")
```

It Seems to be pretty uniform Though it might be a little left skewed, the difference isn't very large is probbably not worth mentioning.

# 3. What is the distribution of US conversions by month? (boxplots or histogram)

```{r}
conversionsByMonth = mutate(conversions, datestamp = month(datestamp))
usConversionsByMonth = filter(conversionsByMonth, country_code == "us") %>% group_by(datestamp) %>% summarise(tot_con = sum(conversions, na.rm = TRUE))

ggplot(usConversionsByMonth, aes(x=datestamp, y=tot_con)) +
  geom_bar(stat = "identity")
```

Looks pretty uniform to me dog. Though it is right skewed. Apparantly this isn't the data for a full year.

# 4. Fit a linear regression model with daily US convsersions as your response (total across all marketing channels) and Day of week (i.e., Mon - Fri) as the covariate. What is the coefficient on Monday? What does this mean? 

```{r}
UsConversionsByDay = conversions %>%  mutate(day = wday(datestamp)) %>% filter(country_code == "us") %>% filter(day > 1) %>% filter(day < 7) %>% group_by(datestamp) %>% summarise(tot_con = sum(conversions, na.rm = TRUE)) %>% mutate(day = wday(datestamp))
model = lm(tot_con ~ as.factor(day), UsConversionsByDay)

summary(model)
```

So Monday is the intercept which makes it's coefficient 38,892 which means it expects about 38,892 conversions on monday
